---
title: "Coding Results"
editor_options: 
  chunk_output_type: console
---

This web section contains the results from the first round of coding.

Each party is listed below. You can drill into each code by starting with the ID column and clicking on a policy item. This will reveal the coders' estimates of the party's position. By clikcing on the Coder column, you will get more detailed information from the individual coder.

**NOTE** A couple of cells seems to be out of sync. Specifically, for the following party X coder combinations: 

- PSD = coder 10 

- UDMR = coder 4

- USR = coder 4

<br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r,message=FALSE,warning=FALSE}
library(here)
#library(janitor)
library(tidyverse)
library(rstatix)
library(kableExtra)
library(ggplot2)
library(ggpubr)
library(DT)
library(reactable)
library(htmltools)

# df <- df %>% 
#   select(-c(party,Dimensiune)) %>% 
#   unite("id", c(ID,Item),sep = ") ") %>% 
#   relocate(coder, .before = `Sursa`)


# df %>% 
#   reactable(groupBy = "id",
#             #onClick = "select",
#             pagination = FALSE, 
#             searchable = FALSE,
#             striped = TRUE,
#             columns = list(id = colDef(minWidth =350))
#             )


```


## AUR

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data/AUR/df.rda"))

reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Sursa", "Justificarea", "Comentarii")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  #`Poziția partidului` = colDef(show = FALSE),
  #`Nivel de încredere` = colDef(show = FALSE),
  Sursa = colDef(show = FALSE),
  Justificarea = colDef(show = FALSE),
  Comentarii = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```


<br>

## PMP

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data/PMP/df.rda"))

reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Sursa", "Justificarea", "Comentarii")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  #`Poziția partidului` = colDef(show = FALSE),
  #`Nivel de încredere` = colDef(show = FALSE),
  Sursa = colDef(show = FALSE),
  Justificarea = colDef(show = FALSE),
  Comentarii = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```


<br>

## PNL

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data/PNL/df.rda"))

reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Sursa", "Justificarea", "Comentarii")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  #`Poziția partidului` = colDef(show = FALSE),
  #`Nivel de încredere` = colDef(show = FALSE),
  Sursa = colDef(show = FALSE),
  Justificarea = colDef(show = FALSE),
  Comentarii = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```


<br>

## PSD

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data/PSD/df.rda"))

reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Sursa", "Justificarea", "Comentarii")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  #`Poziția partidului` = colDef(show = FALSE),
  #`Nivel de încredere` = colDef(show = FALSE),
  Sursa = colDef(show = FALSE),
  Justificarea = colDef(show = FALSE),
  Comentarii = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```


<br>

## REPER

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data/REPER/df.rda"))

reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Sursa", "Justificarea", "Comentarii")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  #`Poziția partidului` = colDef(show = FALSE),
  #`Nivel de încredere` = colDef(show = FALSE),
  Sursa = colDef(show = FALSE),
  Justificarea = colDef(show = FALSE),
  Comentarii = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```


<br>

## UDMR

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data/UDMR/df.rda"))

reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Sursa", "Justificarea", "Comentarii")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  #`Poziția partidului` = colDef(show = FALSE),
  #`Nivel de încredere` = colDef(show = FALSE),
  Sursa = colDef(show = FALSE),
  Justificarea = colDef(show = FALSE),
  Comentarii = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```


<br>

## USR

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data/USR/df.rda"))

reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Sursa", "Justificarea", "Comentarii")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  #`Poziția partidului` = colDef(show = FALSE),
  #`Nivel de încredere` = colDef(show = FALSE),
  Sursa = colDef(show = FALSE),
  Justificarea = colDef(show = FALSE),
  Comentarii = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```


<br>
